---
title: "From 0 to Web App with Shiny"
subtitle: 💅
author: "Emily Bartha, Data Scientist at HomeAway"
runtime: shiny
output: html
_document---

# Installing Shiny

In RStudio, run

```{r, eval = FALSE} 
install.packages(shiny)
```

<br/>

Then navigate to **New File > Shiny Web App...** and name the app whatever you like.

Click **Create**.

# Components of a Shiny app

The User Interface (UI)

- The visual part of your app (what the user sees and interacts with)

- Renders in a web browser

- Under the hood, its Javascript, HTML, and CSS

The Server

- The backend of your web app

- Performs computations and generates the data that the user sees

- Just R code

# The User Interface (UI)

# fluidPage

- Defines the page as a series of rows, allowing the user to specify components which lie on the same line

- Scale in realtime to fill available space

- Each row contains 12 columns of equal width

```{r}
library(shiny)

# Define UI for application that draws a histogram
ui <- fluidPage(
   
   # Application title
   titlePanel("Old Faithful Geyser Data"),
   
   # Sidebar with a slider input for number of bins 
    fluidRow(
       column(width = 3,
              sliderInput("bins",
                   "Number of bins:",
                   min = 1,
                   max = 50,
                   value = 30)),
       column(width = 9,
              plotOutput("distPlot"))
    )
)

# Define server logic required to draw a histogram
server <- function(input, output) {
   
   output$distPlot <- renderPlot({
      # generate bins based on input$bins from ui.R
      x    <- faithful[, 2] 
      bins <- seq(min(x), max(x), length.out = input$bins + 1)
      
      # draw the histogram with the specified number of bins
      hist(x, breaks = bins, col = 'darkgray', border = 'white')
   })
}

# Run the application 
shinyApp(ui = ui, server = server)
```

# UI Layouts

- sidebarLayout - 

# HTML Tags

# Widgets

# Advanced

# The Server

# Inputs and Outputs
